Nuclei Segmentation in Histopathology images using Deep Neural Networks

### 2016-11-07 Paper.tex
ensemble

\address{$^{1}$MINES ParisTech, PSL Research University, CBIO - Centre
  de Bioinformatique, 35 rue St Honoré 77300 Fontainebleau, France; 
$\quad ^{2}$Institut Curie, 75248 Paris Cedex, France; 
$\quad ^{3}$INSERM U900, 75248 Paris Cedex, France; 
$\quad ^{4}$Service de Pathologie, Institut Curie, 75248 Paris Cedex,
France;
$\quad ^{5}$Residual Tumor \& Response to Treatment Laboratory,
RT2Lab, Translational Research Department, Institut Curie, 26, rue d’Ulm, Paris, F-75248, France;
$\quad ^{6}$U932, Immunity and Cancer, INSERM, Institut Curie, Paris, F-75248, France;
$\quad ^{7}$Department of Surgery, Institut Curie, Paris, F-75248, France.
}
%
\begin{document}
%\ninept
%
\maketitle
%
\begin{abstract}
Analysis and interpretation of stained tumor sections is one of the
main tools in cancer diagnosis and prognosis, which is mainly carried
out manually by pathologists. The avent of digital pathology provides
us with the challenging opportunity to automatically analyze large
amounts of these complex and large image data in order to draw
biological conclusions from them and to study cellular and tissular
phenotypes at a large scale. One of the bottlenecks for such an
approach is the automatic segmentation of cell nuclei from this type
of image data. Here, we present a fully automated workflow to segment
nuclei from histopathology image data by training a deep neural
network on a set of annotated images and by proposing a postprocessing
step of the posterior probability maps to split jointly segmented
nuclei. Further, we provide the image data set that has been generated
for this study as a benchmark set to the scientific community.  
\end{abstract}
%
\begin{keywords}
Deep Learning, Convolutional Neural Networks, Nuclei Segmentation,
Histopathology, Digital Pathology, Breast Cancer, Cellular Phenotyping
\end{keywords}
%
\section{Introduction}
\label{sec:intro}

@@

%
%
\begin{minipage}[b]{0.32\linewidth}
  \centering
  \centerline{\includegraphics[height=2.4cm]{DeconvNetB}}
%  \vspace{1.5cm}
  \centerline{DeconvNet}\medskip
\end{minipage}
\hfill
\begin{minipage}[b]{.32\linewidth}
  \centering
  \centerline{\includegraphics[height=2.4cm]{DeconvNetP}}
%  \vspace{1.5cm}
  \centerline{Probability map}\medskip
\end{minipage}
\hfill
\begin{minipage}[b]{.32\linewidth}
  \centering
  \centerline{\includegraphics[height=2.4cm]{DeconvNet_WS}}
%  \vspace{1.5cm}
  \centerline{Watershed}\medskip
\end{minipage}
%
\begin{minipage}[b]{0.32\linewidth}
  \centering
  \centerline{\includegraphics[height=2.4cm]{FCNB}}
%  \vspace{1.5cm}
  \centerline{FCN}\medskip
\end{minipage}
\hfill
\begin{minipage}[b]{.32\linewidth}
  \centering
  \centerline{\includegraphics[height=2.4cm]{FCNP}}
%  \vspace{1.5cm}
  \centerline{Probability map}\medskip
\end{minipage}
\hfill
\begin{minipage}[b]{.32\linewidth}
  \centering
  \centerline{\includegraphics[height=2.4cm]{FCN_WS}}
%  \vspace{1.5cm}
  \centerline{Watershed}\medskip
\end{minipage}
%
\caption{Prediction via different classifiers of a random sample on the left out patient: 581910}
\label{fig:prediction}
%
\end{figure}

>>>>

\address{$^{1}$MINES ParisTech, PSL Research University, CBIO - Centre
  de Bioinformatique,\\ 
  35 rue St Honoré 77300 Fontainebleau, France \\
$^{2}$Institut Curie, 75248 Paris Cedex, France\\
$^{3}$INSERM U900, 75248 Paris Cedex, France\\
$^{4}$Service de Pathologie, Institut Curie, 75248 Paris Cedex, France}
%
\begin{document}
%\ninept
%
\maketitle
%
\begin{abstract}
%The abstract should appear at the top of the left-hand column of text, about
%0.5 inch (12 mm) below the title area and no more than 3.125 inches (80 mm) in
%length.  Leave a 0.5 inch (12 mm) space between the end of the abstract and the
%beginning of the main text.  The abstract should contain about 100 to 150
%words, and should be identical to the abstract text submitted electronically
%along with the paper cover sheet.  All manuscripts must be in English, printed
%in black ink.
\end{abstract}
%
\begin{keywords}
Deep Learnnig, Convolutional Neural Networks, Nuclei Segmentation,
Histpathology, Digital Pathology, Breast Cancer, Cellular Phenotyping
\end{keywords}
%
\section{Introduction}
\label{sec:intro}

@@

%
%
\begin{minipage}[b]{0.32\linewidth}
  \centering
  \centerline{\includegraphics[height=2.4cm]{DeconvNetB}}
%  \vspace{1.5cm}
  \centerline{DeconvNet}\medskip
\end{minipage}
\hfill
\begin{minipage}[b]{.32\linewidth}
  \centering
  \centerline{\includegraphics[height=2.4cm]{DeconvNetP}}
%  \vspace{1.5cm}
  \centerline{Probability map}\medskip
\end{minipage}
\hfill
\begin{minipage}[b]{.32\linewidth}
  \centering
  \centerline{\includegraphics[height=2.4cm]{DeconvNet_WS}}
%  \vspace{1.5cm}
  \centerline{Watershed}\medskip
\end{minipage}
%
\begin{minipage}[b]{0.32\linewidth}
  \centering
  \centerline{\includegraphics[height=2.4cm]{FCNB}}
%  \vspace{1.5cm}
  \centerline{FCN}\medskip
\end{minipage}
\hfill
\begin{minipage}[b]{.32\linewidth}
  \centering
  \centerline{\includegraphics[height=2.4cm]{FCNP}}
%  \vspace{1.5cm}
  \centerline{Probability map}\medskip
\end{minipage}
\hfill
\begin{minipage}[b]{.32\linewidth}
  \centering
  \centerline{\includegraphics[height=2.4cm]{FCN_WS}}
%  \vspace{1.5cm}
  \centerline{Watershed}\medskip
\end{minipage}
%
\begin{minipage}[b]{0.32\linewidth}
  \centering
  \centerline{\includegraphics[height=2.4cm]{EnsembleB}}
%  \vspace{1.5cm}
  \centerline{Ensemble}\medskip
\end{minipage}
\hfill
\begin{minipage}[b]{.32\linewidth}
  \centering
  \centerline{\includegraphics[height=2.4cm]{EnsembleP}}
%  \vspace{1.5cm}
  \centerline{Probability map}\medskip
\end{minipage}
\hfill
\begin{minipage}[b]{.32\linewidth}
  \centering
  \centerline{\includegraphics[height=2.4cm]{Ensemble_WS}}
%  \vspace{1.5cm}
  \centerline{Watershed}\medskip
\end{minipage}
\caption{Prediction via different classifiers of a random sample on the left out patient: 581910}
\label{fig:prediction}
%
\end{figure}
